---
title: "Multinormal Density in R code"
author: "AngeloPStats"
date: "2022-04-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***Let's start by downloading two main packages in R Studio***

*Plots 3D*

```{r warning=FALSE}

install.packages("plot3D")

library(plot3D)

```


*Computes multivariate normal densities*

```{r warning=FALSE}
install.packages("mvtnorm")

library(mvtnorm)

```

*Now, to set up our grid-2D we can create a range of values of x1 and x2*

```{r warning=FALSE}
x1 = seq(-pi/4, pi/4, len=30)

x2 = seq(pi/4,3*pi/4, len=30)

```


*This is because the normal density varies from -3 to 3, approximately*

*The next step is to form two 2D functions to get a 3D plot*

```{r warning=FALSE}
f.function = function(x1,x2){cos(x1*x2)}

h.function = function(x1,x2){1-((pi*x1)^2)/8}

```

*Now we can use "persp3D" and "outer". *

*They are part of the previously downloaded package*

**Plot in 3D**

```{r warning=FALSE}

zf.function = outer(x1,x2,f.function )

zh.function = outer(x1,x2,h.function )

```


*This is to organize the plots in a matrix view*

```{r warning=FALSE}

par(mfrow = c(1,2))

```

*color surface of f is red*

```{r warning=FALSE}
persp3D(x1,x2,zf.function,col = "red", main="f function surface")

persp3D(x1,x2,zh.function,col = "blue", main="h function surface")

```

*.rmd linguist-language=R *